Quality assurance of digital twins: An experience report in the automotive industry

### 2023-07-04 manuscripts/paper-1/Without_Names.tex
1.review corrected

    \textbf{Efficiency} refers to the quality of being efficient~\cite{OxfordDictionary}. 
    Therefore, \textit{efficiency} is achieving maximum productivity with minimum wasted resources (Figure~\ref{fig:EfficiencyandFidelity}). 
    It is worth mentioning that the concept of \textit{efficiency} is tightly coupled with the notion of productivity, 
    although \textit{efficiency} differs from the latter's definition, which is defined as the capability to produce large amounts of goods~\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired (Figure~\ref{fig:EfficiencyandFidelity}).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1\textwidth]{Efficiency and Fidelity.png}
        \caption{Fidelity and efficiency levels have been demonstrated with simplified CAD drawings.}~\label{fig:EfficiencyandFidelity}
    \end{figure}

>>>>

    \textbf{Efficiency} refers to the quality of being efficient~\cite{OxfordDictionary}. 
    Therefore, \textit{efficiency} is achieving maximum productivity with minimum wasted resources (Figure~\ref{fig:EfficiencyandFidelity}). 
    It is worth mentioning that the concept of \textit{efficiency} is tightly coupled with the notion of productivity, 
    although \textit{efficiency} differs from the latter's definition, which is defined as the capability to produce large amounts of goods~\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired (Figure~\ref{fig:EfficiencyandFidelity}).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.9\textwidth]{Efficiency and Fidelity.png}
        \caption{Fidelity and Efficiency levels have been demonstrated with simplified CAD drawings. For the assessment of 
        Efficiency, quantitative metrics, rendering time, and model size have been utilized.}~\label{fig:EfficiencyandFidelity}
    \end{figure}
